Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-17 paper/main.tex
oops, comment was on wrong figure

\textcolor{red}{(We need to fix the entire previous paragraph. How about we keep it short
and sweet and say we considered a Matern kernel, but found that the spatial correlation
decayed so quickly ($\theta\rightarrow 0$) that spatial dependence was not necessary.)}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_fit.png}
    \caption{95\% credible intervals for the power spectrum of model 1 (posterior mean 
             subtracted). Plots of the perturbation theory, low-resolution and high-resolution 
             runs are also shown, alongside the weighted average.
             \textcolor{red}{(This plot needs to be made fresh (not using the package
             function.  Adjust y-axis.  We don't need the yellow/red coloring.)}}
    \label{fig:plot_fit}
\end{figure}

\begin{figure}[ht]
   \centering
   \includegraphics[width=6in]{plot_warp_M001.png}
   \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. 
            Right: Corresponding 95\% credible intervals for $W$, where departure 
            from the identity line represents nonstationary behavior.}
   \label{fig:plot_warp}
\end{figure}

>>>>

\textcolor{red}{(We need to fix the entire previous paragraph. How about we keep it short
and sweet and say we considered a Matern kernel, but found that the spatial correlation
decayed so quickly ($\theta\approx 0$) that spatial dependence was not necessary.)}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_fit.png}
    \caption{95\% credible intervals for the power spectrum of model 1 (posterior mean 
             subtracted). Plots of the perturbation theory, low-resolution and high-resolution 
             runs are also shown, alongside the weighted average.}
    \label{fig:plot_fit}
\end{figure}

\begin{figure}[ht]
   \centering
   \includegraphics[width=6in]{plot_warp_M001.png}
   \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. 
            Right: Corresponding 95\% credible intervals for $W$, where departure 
            from the identity line represents nonstationary behavior.
            \textcolor{red}{(This plot needs to be made fresh (not using the package
             function.  Adjust y-axis.  We don't need the yellow/red coloring.)}}
   \label{fig:plot_warp}
\end{figure}
